---
title: "Available Datasets"
description: >
   A concise overview about the 315 datasets from the OGD portal which are compatible with STATcubeR.
   Learn how to discover useful datasets and read OGD metadata.
link_text: "available datasets article"
---

```{r, echo=FALSE}
source("R/setup.R")$value
```

```{r, include=FALSE}
library(reactable)
library(tidyverse)
all_datasets <- od_list()
```

At the time of writing this article, there are 315 datasets that are assumed to be compatible with `od_table()`.

## Interactive overview

Since some of the metadata contained in the OGD JSON files is only available in German, the following overview uses German labels.
Click on the individual table cells to get more information.

```{r, echo = FALSE}
ids <- all_datasets$id
## <- timestamp=NULL means reuse available jsons
jsons <- lapply(ids, od_json, NULL)
od_index <- tibble(
  ## general
  label = map_chr(jsons, "title"),
  description = map_chr(jsons, "notes"),
  ## timing
  resource = map(jsons, "resources") %>% map(1),
  last_modified = map_chr(resource, "last_modified") %>%
    as.POSIXct(format = "%Y-%m-%dT%H:%M:%OS"),
  created = map_chr(resource, "created") %>% as.POSIXct(format = "%Y-%m-%dT%H:%M:%OS"),
  update_frequency = map_chr(jsons, c("extras", "update_frequency")),
  ## tags and categories
  categories = map(jsons, c("extras", "categorization")) %>% map(unlist),
  tags = map(jsons, "tags") %>% map(unlist),
  id_sc = map(jsons, c("extras", "metadata_linkage")) %>% map(1) %>%
    map_if(~ grepl("statcube", .x), ~ strsplit(.x, "=")[[1]][2], .else = ~ "") %>%
    map_chr(1),
  id_od = map_chr(resource, "name")
) %>% select(-resource)

descs_parsed <- map(jsons, STATcubeR:::od_attr)
od_index$measures <- lapply(descs_parsed, function(x) {
  x[substr(x$code, 1, 1) == "F", ]
})

od_index$fields <- lapply(descs_parsed, function(x) {
  x[substr(x$code, 1, 1) == "C", ]
})

## rendering
hide_col <- colDef(show = FALSE)
tpy <- function(x, y) {
  tags$span(x, `data-tippy-content` = y)
}

od_index %>%
  mutate(
    n_fields = purrr::map_int(fields, nrow),
    n_measures = purrr::map_int(measures, nrow)
  ) %>%
  reactable(
    columns = list(
      label = colDef(
        name = "Bezeichnung", html = TRUE,
        details = JS("od_table.details.label")
      ),
      description = hide_col,
      last_modified = colDef(
        name = "Stand", width = 90, align = "right",
        cell = JS("od_table.parse_time"), html = TRUE,
        header = function(value) {tpy(value, "Zeitpunkt der letzten Aktualisierung")},
        details = JS("od_table.details.last_modified")
      ),
      created = hide_col,
      update_frequency = hide_col,
      categories = colDef(
        name = "Kat.", width = 70, html = TRUE,
        header = function(value) { tpy(value, "Primäre Kategorie des Datensatzes") },
        cell = function(value) {
          value[[1]] %>% switch(
            Arbeit = "ARB", Bevölkerung = "BEV", `Bildung und Forschung` = "B&F",
            `Finanzen und Rechnungswesen` = "F&R", `Geographie und Planung` = "G&P",
            `Gesellschaft und Soziales` = "G&S", Gesundheit = "GES", Umwelt = "UMW",
            `Verkehr und Technik` = "V&T", `Wirtschaft und Tourismus` = "W&T") %>%
            tpy(value[[1]])
        },
        details = JS("od_table.details.category")
      ),
      tags = hide_col,
      id_sc = hide_col,
      id_od = hide_col,
      measures = hide_col,
      fields = hide_col,
      n_measures = colDef(
        name = "M", width = 50, html = TRUE,
        header = function(x) {tpy("M", "Messwerte")},
        details = reactable::JS("od_table.details.measures")
      ),
      n_fields = colDef(
        name = "K", width = 50, html = TRUE,
        header = function(x) {tpy("K", "Klassifikationen")},
        details = JS("od_table.details.fields")
      )
    ),
    wrap = FALSE, searchable = TRUE, striped = TRUE, minRows = 10, highlight = TRUE
  ) %>% htmlwidgets::appendContent(
    htmltools::includeCSS("od_list/od_reactable.css"),
    htmltools::includeScript("od_list/od_reactable.js"))
```

## CLI usage

To get a simplified version of this summary, use the `od_list()` function.
It uses webscraping techniques to get dataset ids and German labels based on the contents of https://data.statistik.gv.at/web/catalog.jsp.

```{r, eval = FALSE}
all_datasets <- od_list()
all_datasets
```

```{r, echo = FALSE}
all_datasets
```

## Overview via json

If you identify an interesting dataset, consider downloading the metadata json to get more details.
The json contains links to further metadata including a link to `r ogd_portal`.

```{r}
(id <- all_datasets$id[2])
json <- od_json(id)
json
```

This output is generated from `r style_resource(id, ext = "json")` and shows a summary of the available metadata. Other parts of the metadata can be extracted with `$` using the keys from the json specification.

```{r}
json$extras$update_frequency
```

## Showcase {.tabset .tabset-pills .tabset-fade}

### Population

```{r, include = FALSE}
x <- od_table("OGD_bevstandjbab2002_BevStand_2020")
```

The `r tippy_dataset(x, "population dataset")` measures the Austrian population
for `r nrow(x$field("Commune"))` different regions.

```{r}
od_table("OGD_bevstandjbab2002_BevStand_2020")$tabulate()
```

### Hospitalizations

```{r, include = FALSE}
x <- od_table("OGD_krankenbewegungen_ex_LEISTUNGEN_1")
```

The `r tippy_dataset(x, "hospitalizations dataset")` is a timeseries from 2009 to 2019
for `r nrow(x$field("Med"))` different medical procedures.

```{r}
od_table("OGD_krankenbewegungen_ex_LEISTUNGEN_1")$tabulate()
```

### Earnings

```{r, include = FALSE}
x <- od_table("OGD_veste309_Veste309_1")
```

The `r tippy_dataset(x, "structure of earnings dataset")` showcases average earnings by four different classifications.
See the `r ticle("sc_tabulate")` for some usage examples with this dataset.

```{r}
od_table("OGD_veste309_Veste309_1")$tabulate()
```

### Household forecast

```{r, include=FALSE}
x <- od_table("OGD_f1741_HH_Proj_2")
```

The `r tippy_dataset(x, "household forecast")` contains predictions about the
number of private households by 4 household characteristics from 2011 to 2080.

```{r}
od_table("OGD_f1741_HH_Proj_2")$tabulate()
```

### Gross regional product

```{r, include=FALSE}
x <- od_table("OGD_vgrrgr104_RGR104_1")
```

The `r tippy_dataset(x, "GRP dataset")` contains GRP for all NUTS-3 regions between 2000 and 2019.

```{r}
od_table("OGD_vgrrgr104_RGR104_1")$tabulate()
```
