---
title: "Open Government Data"
description: >
  Hands-on guide on how to get and use datasets from the OGD portal.
  This article also contains a short introduction on tabulation and translation of datasets.
link_text: OGD article
---

```{r, echo = FALSE}
source("R/setup.R")$value
```

```{r, include = FALSE}
table <- od_table("OGD_krebs_ext_KREBS_1")
```

`od_table()` makes it easy to import datasets from `r ogd_portal` into your R sessions.
This function downloads csv sources from the fileserver.
This means that no API key is required to use STATcubeR with datasets from the OGD portal.

In this example, we will use a `r tippy_dataset(table, "data set about cancer statistics")`.
The dataset id `"OGD_krebs_ext_KREBS_1"` can be extracted from the url and will be used in the data import.

```{js, echo = FALSE}
let url = "https://data.statistik.gv.at/"
tippy("#ogd", {allowHTML: true, interactive: true, theme: 'light rounded', content: 
  "<b>Open Government Data from Statistics Austria</b><br/>" +
  "The open data portal provides datasets from Statistics Austria" +
  " according to open data guidelines<br/>" +
  `<a href=${url} target='blank_'>${url}</a>`
})
```

## Import and overview

To import a dataset, provide the dataset id as an argument.

```{r, message=FALSE}
table <- od_table("OGD_krebs_ext_KREBS_1")
```

This returns an object of class [`od_table`], which bundles all the data from the OGD portal that correspons to this dataset.
Printing the object will show a summary of the contents. 

```{r}
table
```

The dataset contains the number of cancer patients by several classification fields

- **tumor type** differentiates **<95>** types of cancers
- The **reporting period** spans **<37>** years (1983 to 2019).
- The **regional** variable contains the **<9>** NUTS-2 regions of austria.
- The **demographic** variable "Sex" is reported with **<2>** levels

## Convert to a data frame

The method `$tabulate()` can be used to turn the object into a `data.frame` in long format,
which contains labled data.

```{r}
table$tabulate()
```

The dataset contains `r nrow(table$data)` rows. 
If every combination of tumor type, year, region and sex would contain a seperate row the number of rows would be the following.

\[
95\times37\times9\times2 = 63270
\]

This means that the table is fairly dense. But this might not be the case for other OGD datasets.

## Metadata

This section will show the different metadata components contained in the table object and how they relate to the resources on the OGD server.

```{r, collapse=TRUE}
table$resources$name
```

### Header

The labels for the columns of the data.frame representation are generated from `r style_resource("OGD_krebs_ext_KREBS_1", "HEADER")` and can be extracted from the table object via `$header`. 

```{r}
table$header
```

Additional metadata for the columns can be obtained via `$meta`.
See the `r ticle("sc_data")` for more details.

### Field infos {.unlisted .unnumbered .tabset .tabset-pills}

```{r, include=FALSE}
options(tibble.print_max = 5)
options(tibble.print_min = 5)
```

The method `table$field()` can be used to get information about specific classification fields.
Thise contain data from `{dataset_id}_{field_code}.csv`.
Unlike the metadata in `sc_table`, the `od_table` class always contains german and english labels.
Both can be used to label the dataset.

#### Tumor type

The following call gives access to the german and english labels for the 95 differen tumor types in the `"cancer type"` classification. 
Click `"Year"` above to see information about the years.

```{r}
table$field("C-TUM_ICD10_3ST-0")
```

`r style_resource("OGD_krebs_ext_KREBS_1", "C-TUM_ICD10_3ST-0")`


#### Year

The reporting period spans 37 years (1983 to 2019).
The classification elements are parsed into a `<date>` format for the `<data.frame>` representation.

```{r}
table$field("C-BERJ-0")
```

`r style_resource("OGD_krebs_ext_KREBS_1", "C-BERJ-0")`

#### Province

The regional classification contains 9 elements which correspond to the NUTS2 regions ("Bundesländer") of austria.

```{r}
table$field("C-BUNDESLAND-0")
```

`r style_resource("OGD_krebs_ext_KREBS_1", "C-BUNDESLAND-0")`

#### Sex

Sex is coded as a ditochome variable with the classification elements `"male"` and `"female"`.

```{r}
table$field("C-KRE_GESCHLECHT-0")
```

`r style_resource("OGD_krebs_ext_KREBS_1", "C-KRE_GESCHLECHT-0")`

### json Metadata {.tabset .tabset-pills}

The json metadatafile `r style_resource("OGD_krebs_ext_KREBS_1", ext = "json")` is available via the `$json` binding.

#### Cancer

```{r}
table$json
```

#### Earnings

```{r}
od_json("OGD_veste309_Veste309_1")
```

#### Economic Trend Monitor

```{r}
od_json("OGD_konjunkturmonitor_KonMon_1")
```


###

This print method only shows part of the metadata. More information can be extracted by using the keys of the json object.

```{r, collapse=TRUE}
table$json$extras$publisher
table$json$extras$update_frequency
table$json$resources[[1]]$url
```

## Table Contents

To get the raw microdata from `r style_resource("OGD_krebs_ext_KREBS_1")`, use `table$data`.
The output is similar to what is returned from `read.csv2("OGD_krebs_ext_KREBS_1.csv")`.

```{r}
table$data
```

`od_table()` makes sure that the levels of all factor columns are in the same order as in the metadata.

```{r}
levels(table$data$`C-BUNDESLAND-0`) == table$field("C-BUNDESLAND-0")$code
```

As mentioned above, a labelled version of the data can be obtained via `table$tabulate()`. 
The labelling is done by taking the raw dataset and then joining the labes from `$header` and `$field()`.

```{r}
table$tabulate()
```

Time variables are converted into a `<date>` format if they satisfy certain STATcube standards.
You can read more about `$tabulate()` in the `r ticle('sc_tabulate')`.

## A Trip to Germany {#sauerkraut}

It is possible to switch the language used for labelling the dataset using the `$language` field.
This field can be used to get and set the language.
Allowed options are `"en"` for english and `"de"` for german.

```{r, collapse=TRUE}
table$language
table$language <- "de"
table$language
```

This option affects the `print()` method as well as the output of `$tabulate()`.
If no english labels are available, the german labels are used as a fallback mechanism.

```{r}
table
```

```{r}
table$tabulate()
```

## Further reading

* See the `r ticle('od_list')` to list all datasets that are compatible with `od_table()`.
* Open data datasets often contain a large amount of rows.
  Check out the `r ticle('sc_tabulate')` to see how they can be summarized into a more compact form.
* `r STATcubeR` caches all files requested from the server under the hood.
  The `r ticle('od_resources')` explains where and how those caches are stored.
  

[`od_table`]: ../reference/od_table_class.html
