---
title: "Open Government Data"
description: Overview about all functionalities regarding OGD Datasets
---

```{r, include = FALSE}
pkgload::load_all(export_all = FALSE, reset = FALSE, helpers = FALSE) 
source("R/df_print.R")
source("R/add_tooltip.R")
od_cache_dir("~/.cache/STATcubeR/open_data/")
```

`od_table()` makes it easy to import datasets from the <u id='ogd'>open data portal</u> into your R sessions.
This function does use direct downloads from the fileserver.
Therefore no API key is required.

In this example, we will use a <u id='cancer_data'>data set about cancer statistics</u>.
The dataset id `OGD_krebs_ext_KREBS_1` can be extracted from the url and will be used in the data import.

```{r, echo = FALSE}
htmltools::tagList(
  add_tooltip(
    "ogd", "https://data.statistik.gv.at/",
    "The open data portal provides datasets from Statistics Austria according to open data guidelines"
  ),
  add_tooltip(
    "cancer_data", "https://data.statistik.gv.at/web/meta.jsp?dataset=OGD_krebs_ext_KREBS_1",
    "Cancer statistics by reporting year, province of residence and localisation of cancer"
  )
)
```

## Import

To import a dataset, provide the dataset id as an argument.

```{r, message=FALSE}
table <- od_table("OGD_krebs_ext_KREBS_1")
```

The returned object is of class [`od_table`].
It provides an overview of the dataset via the `print()` method. 

```{r}
table
```

## Metadata

Information from [`OGD_krebs_ext_KREBS_1_HEADER.csv`] can be obtained via `$header`. 

```{r}
table$header
```

Additional metadata can be obtained via `$meta`.
See the metadata article for more details.

The method `table$field()` can be used to get information about specific fields.
For example, the information from [`OGD_krebs_ext_KREBS_1_C-KRE_GESCHLECHT-0.csv`] is available through this call.

```{r}
table$field("C-KRE_GESCHLECHT-0")
```

Unlike the metadata in `sc_table`, the `od_table` class always contains german and english labels.
Both can be used to label the dataset.

## Table Contents

To get the actual microdata from [`OGD_krebs_ext_KREBS_1.csv`], use `table$data`.
The output is similar to what is returned from `read.csv2("OGD_krebs_ext_KREBS_1.csv")`.

```{r}
table$data
```

`od_table()` makes sure that the levels of all factor columns are in the same order as in the metadata.

```{r}
levels(table$data$`C-BUNDESLAND-0`) == table$field("C-BUNDESLAND-0")$code
```

If you want to use labels rather than codes, a labelled version of the data can be obtained via `table$tabulate()`. 
The labelling is done by mapping codes to english names using the previsously mentioned metadata.

```{r}
table$tabulate()
```

Time variables are converted into a `<date>` format if they satisfy certain STATcube standards.
You can read more about `$tabulate()` in the [tabulation article].

## A Trip to Germany {#sauerkraut}

It is possible to switch the language used for labelling the dataset using the `$language` field.
This field can be used to get and set the language.
Allowed options are `"en"` for english and `"de"` for german.

```{r}
table$language
table$language <- "de"
```

This option affects the print method as well as the output of `$data`.
If no english labels are available, the german labels are used as a fallback mechanism.

```{r}
table
```

```{r}
table$tabulate()
```

## Further reading

* See the [available datasets article] to list all datasets that are compatible with `od_table()`.
* Open data datasets often contain a large amount of rows.
  Check out the [tabulation article] to see how they can be summarized into a more compact form.
* `{STATcubeR}` caches all files requested from the server under the hood.
  The [caching article] explains where and how those caches are stored.

[caching article]: od_resources.html
[available datasets article]: od_list.html
[tabulation article]: od_tabulate.html
[`od_table`]: ../reference/od_table_class.html
[`OGD_krebs_ext_KREBS_1.csv`]: https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1.csv
[`OGD_krebs_ext_KREBS_1_HEADER.csv`]: https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1_HEADER.csv
[`OGD_krebs_ext_KREBS_1_C-KRE_GESCHLECHT-0.csv`]: https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1_C-KRE_GESCHLECHT-0.csv
