---
title: "Open Government Data"
description: Overview about all functionalities regarding OGD Datasets
link_text: OGD article
---

```{r, echo = FALSE}
source("R/setup.R")$value
```

```{r, include = FALSE}
table <- od_table("OGD_krebs_ext_KREBS_1")
```

`od_table()` makes it easy to import datasets from `r ogd_portal` into your R sessions.
This function uses direct downloads from the fileserver.
Therefore no API key is required.

In this example, we will use a `r tippy_dataset(table, "data set about cancer statistics")`.
The dataset id `OGD_krebs_ext_KREBS_1` can be extracted from the url and will be used in the data import.

```{js, echo = FALSE}
let url = "https://data.statistik.gv.at/"
tippy("#ogd", {allowHTML: true, interactive: true, theme: 'light rounded', content: 
  "<b>Open Government Data from Statistics Austria</b><br/>" +
  "The open data portal provides datasets from Statistics Austria" +
  " according to open data guidelines<br/>" +
  `<a href=${url} target='blank_'>${url}</a>`
})
```

## Import

To import a dataset, provide the dataset id as an argument.

```{r, message=FALSE}
table <- od_table("OGD_krebs_ext_KREBS_1")
```

The returned object is of class [`od_table`].
It provides an overview of the dataset via the `print()` method. 

```{r}
table
```

## Metadata

Information from [`OGD_krebs_ext_KREBS_1_HEADER.csv`] can be obtained via `$header`. 

```{r}
table$header
```

Additional metadata can be obtained via `$meta`.
See the `r ticle("sc_data")` for more details.

### Field infos {.unlisted .unnumbered .tabset .tabset-pills}

```{r, include=FALSE}
options(tibble.print_max = 5)
options(tibble.print_min = 5)
```


The method `table$field()` can be used to get information about specific fields.
Thise contain data from `{dataset_id}_{field_code}.csv`.
Unlike the metadata in `sc_table`, the `od_table` class always contains german and english labels.
Both can be used to label the dataset.

#### Tumor type

```{r}
table$field("C-TUM_ICD10_3ST-0")
```

https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1_C-TUM_ICD10_3ST-0.csv

#### Year

```{r}
table$field("C-BERJ-0")
```

https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1_C-BERJ-0.csv

#### Province

```{r}
table$field("C-BUNDESLAND-0")
```

https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1_C-BUNDESLAND-0.csv

#### Sex

```{r}
table$field("C-KRE_GESCHLECHT-0")
```

https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1_C-KRE_GESCHLECHT-0.csv

## Table Contents

To get the actual microdata from [`OGD_krebs_ext_KREBS_1.csv`], use `table$data`.
The output is similar to what is returned from `read.csv2("OGD_krebs_ext_KREBS_1.csv")`.

```{r}
table$data
```

`od_table()` makes sure that the levels of all factor columns are in the same order as in the metadata.

```{r}
levels(table$data$`C-BUNDESLAND-0`) == table$field("C-BUNDESLAND-0")$code
```

If you want to use labels rather than codes, a labelled version of the data can be obtained via `table$tabulate()`. 
The labelling is done by mapping codes to english names using the previsously mentioned metadata.

```{r}
table$tabulate()
```

Time variables are converted into a `<date>` format if they satisfy certain STATcube standards.
You can read more about `$tabulate()` in the `r ticle('sc_tabulate')`.

## A Trip to Germany {#sauerkraut}

It is possible to switch the language used for labelling the dataset using the `$language` field.
This field can be used to get and set the language.
Allowed options are `"en"` for english and `"de"` for german.

```{r}
table$language
table$language <- "de"
```

This option affects the `print()` method as well as the output of `$data`.
If no english labels are available, the german labels are used as a fallback mechanism.

```{r}
table
```

```{r}
table$tabulate()
```

## Further reading

* See the `r ticle('od_list')` to list all datasets that are compatible with `od_table()`.
* Open data datasets often contain a large amount of rows.
  Check out the `r ticle('sc_tabulate')` to see how they can be summarized into a more compact form.
* `r STATcubeR` caches all files requested from the server under the hood.
  The `r ticle('od_resources')` explains where and how those caches are stored.
  

[`od_table`]: ../reference/od_table_class.html
[`OGD_krebs_ext_KREBS_1.csv`]: https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1.csv
[`OGD_krebs_ext_KREBS_1_HEADER.csv`]: https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1_HEADER.csv
[`OGD_krebs_ext_KREBS_1_C-KRE_GESCHLECHT-0.csv`]: https://data.statistik.gv.at/data/OGD_krebs_ext_KREBS_1_C-KRE_GESCHLECHT-0.csv
