---
title: "Caching API Responses"
description: >
  STATcubeR can be configured to cache API responses and reuse them later.
  This article describes the necessary setup as well as potential usecases.
link_text: "API cache article"
---

```{r, echo=FALSE}
source("R/setup.R")$value
```

```{r, include=FALSE}
sc_cache_dir("~/.STATcubeR_cache")
```

`r STATcubeR` allows you to cache responses from the STATcube REST API.
This means, for example, that responses for the /table endpoint can be reused.

## Setup

Caching is disabled by default.
In order to activate or deactivate caching, use the functions `sc_cache_enable()` and `sc_cache_disable()`

```{r}
sc_cache_enable()
```

The caching directory can be displayed or changed using `sc_cache_dir()`

```{r}
sc_cache_dir()
sc_cache_dir("~/.cache/STATcubeR/api")
sc_cache_dir()
```

## Using the cache

Caching will affect all calls to `sc_table()` and `sc_schema()` as well as their "derived" functions:
`sc_table_saved()`, `sc_table_custom()`, `sc_schema_db()`, `sc_schema_catalogue()`.

If the same resource is requested several times, the last valid API response is reused.
Invalid resposes (such as 404 responses) will not be added to the cache.

Cache files always contain unparsed API responses as returned by `httr::GET()` or `httr::POST()`.
Responses are stored in an `rds` format.
If caching is enabled, the corresponding cache files to an object of class `sc_schema` or `sc_table` can be retieved using `sc_cache_files()`.

```{r}
sc_example("accomodation") %>% sc_table(language = "both") %>% sc_cache_files()
sc_schema_catalogue() %>% sc_cache_files()
```

Note that the first call to `sc_cache_files()` returned two paths.
Since the table was requested in two languages, two api responses are necessary to construct the table object.

The content of the cache files can be parsed using `readRDS()` and `httr::content()`.
This gives direct access to the API response in a `list()` format.
For example, the following syntax can be used to extract the database info from the response.

```{r}
sc_example("accomodation") %>% sc_table() %>% sc_cache_files() %>%
  readRDS() %>% httr::content() %>% .[["database"]] %>% str()
```

## Cleaning the cache

Cache files can be deleted individually using the paths returned by `sc_cache_files()`.
Alternatively, use `sc_cache_clear()` to delete all files from the cache.

```{r, eval=FALSE}
sc_cache_clear()
#> deleted 12 entries from the cache
```

## Should I use caching?

If you are using `r STATcubeR` interactively, the answer is probably no.
However, when building applications that rely on STATcube data caching can be a usefiul way to decrease the traffic with the STATcube server.
Another usecase for caching is if you are writing `{rmarkdown}` documents that rely on STATcube data.
Caching makes those documents both reproducible and quicker to render.

Please note that there is currently no reliable way to invalidate the cache.
Therefore, API responses will be reused even if resources get updated on the server.
