---
title: "The STATcubeR Data Class"
description: "The base class for Open Data and STATcube datasets"
link_text: "STATcubeR data article"
---

```{r, echo = FALSE}
source("R/setup.R")$value
```

```{r, include = FALSE}
options(tibble.print_min = 5)
```

The class [sc_data] defines a common interface for open data datasets and responses from the `/table` endpoint of the STATcube REST API.
It defines methods that are applicable to both datasources like aquiring metadata, labeling the data and aggregating results.

## Constructing sc_data objects

The [sc_data] class itself is not exported in `r STATcubeR`.
Therefore, objects of the class should be created with one of the following functions

* `od_table()` obtains data from the OGD portal.
  See the `r ticle("od_table")`
* `sc_table()` creates a request against the table endpoint of the STATcube REST API.
  See the `r ticle("sc_table")`
    * `sc_table_saved()` and `sc_table_custom()` also use the `/table` endpoint.
       However, the request is specified via ids rather than a json file.

To illustrate, we will use one of the OGD datasets to showcase the functionalities of this class.
Notice however, that objects created with `sc_table()` can be used interchangibly.

```{r}
x <- od_table("OGD_krebs_ext_KREBS_1")
```

## Data

The data from the table can be extracted using the active binding `$data`.
Notice how `r tippy_dataset(x)` only includes codes and possibly some totals.
The data is always provided in a long format with one column for each field and one column for each measure.

```{r}
x$data
```

It will be explained how labeled data can be obtained in the **Tabulation** section.

## Metadata

Metadata for a [sc_data] object includes labels and other information that is relevant to correctly parse the raw data.
The active binding `$meta` contains at least the entries `$source`, `$measures` and `$fields`.

### Source

The source field contains information about the data source.
The most important entries are `code` and `label`.

```{r}
x$meta$source
```

On the bottom, we see that additional information about the source is available, namely `label_en`, `label_de`, etc.
These metadata were added from the derived class `od_table` and are not part of the `sc_table` interface.

### Measures

This part of the metadata is a data.frame with one row for each measure.
It contains codes and labels as well as the number of NAs found in `$data` for that particular column.

```{r}
x$meta$measures
```

### Fields

The fields entry summarizes all categorical variables.
It includes the codes and labels as well as the total code registered for the particular field.

```{r}
x$meta$fields
```

## Field information

To get more info about specific fields, use the `$field()` method.

### {.tabset .tabset-pills .tabset-fade}

#### Tumor types

```{r}
x$field("Tumore")
```

#### Year

```{r}
x$field("Reporting year")
```

#### Province

```{r}
x$field("Province")
```

#### Sex

```{r}
x$field("Sex")
```

## Tabulation

The method `$tabulate()` can be used to turn `sc_table` objects into tidy data.frames.
See the `r ticle("sc_tabulate")` for more defails.

```{r}
x$tabulate()
```

[sc_data]: ../reference/sc_data.html
