---
title: "The STATcubeR data class"
description: "The base class for Open Data and STATcube datasets"
---

```{r, include = FALSE}
pkgload::load_all()
source("R/df_print.R")
options(tibble.print_min = 5)
od_cache_dir("~/.cache/STATcubeR/open_data/")
```

The class [sc_data] defines a common interface for open data datasets and responses from the `/table` endpoint of the STATcube REST API.
It defines methods that are applicable to both datasources like aquiring metadata, labeling the data and aggregating results.

## Constructing `sc_data` objects

The [sc_data] class itself is not exported in `{STATcubeR}`.
Therefore, objects of the class should be created with one of the following functions

* `od_table()` obtains data from the OGD portal.
* `sc_table()` creates a request against the table endpoint of the STATcube
  REST API
    * `sc_table_saved()` and `sc_table_custom()` also use the `/table` endpoint.
       However, the request is specified via ids rather than a json file.
* `df_table()` creates a [sc_data] object based on a data.frame.
  The function was developed to make STATcubeR data and data frames interchangable for an internal project.

To illustrate, we will use one of the OGD datasets to showcase the functionalities of this class.
Notice however, that objects created with `sc_table()` can be used interchangibly.

```{r}
x <- od_table("OGD_krebs_ext_KREBS_1")
```

## Data

The data from the table can be extracted using the active binding `$data`.
Notice how this dataset only includes codes and possibly some totals.
The data is always provided in a long format with one column for each field and one column for each measure.

```{r}
x$data
```

It will be explained how labeled data can be obtained in the **Tabulation** section.

## Metadata

Metadata for a [sc_data] object includes labels and other information that is relevant to correctly parse the raw data.
The active binding `$meta` contains at least the entries `$source`, `$measures` and `$fields`.

### Source

The source field contains information about the data source.
The most important entries are `code` and `label`.

```{r}
x$meta$source
```

On the bottom, we see that additional information about the source is available, namely `label_en`, `label_de`, etc.
These metadata were added from the derived class `od_table` and are not part of the `sc_table` interface.

### Measures

This part of the metadata is a data.frame with one row for each measure.
It contains codes and labels as well as the number of NAs found in `$data` for that particular column.

```{r}
x$meta$measures
```

### Fields

The fields entry summarizes all categorical variables.
It includes the codes and labels as well as the total code registered for the particular field.

```{r}
x$meta$fields
```

## Tabulation

The method `$tabulate()` can be used to turn `sc_table` objects into tidy data.frames.
See the [tabulation article](od_tabulate.html) for more defails.

```{r}
x$tabulate()
```

[sc_data]: ../reference/sc_data.html
