---
title: "Other REST API Endpoints"
description: >
  How to use the (rather simple) endpoints `/info` and `/rate_limit_table`.
link_text: "other API endpoints article"
---

```{r, echo = FALSE}
source("R/setup.R")$value
```

```{r, include = FALSE}
if (!sc_key_exists())
  knitr::opts_chunk$set(eval = FALSE)
```

Apart form [`/table`] and [`/schema`], there is also support for the simple
endpoints [`/info`] and [`/rate_limit`].
The  [`/info`] endpoint gives and overview about the available languages on the server.

```{r, eval = FALSE}
sc_info()
```

```{r, echo = FALSE}
tibble::tibble(locale = c("de", "en"), displayName = c("Deutsch", "English"))
```


The [`/rate_limit`] endpoint shows the number of calls to the [`/table`]
endpoint that are remaining. 

```{r, eval = FALSE}
sc_rate_limit_table()
```

```{r}
## remaining: 92/100
## reset:     2022-08-30 13:53:55
```

In this case, we see that 8 out of the 100 requests per hour have been used up
and 92 are still available
Th rate limit will be reset once per hour.
In this case this will be at `2022-08-30 13:53:55`.
The entry under reset should always be less than one
hour after the request to the [`/rate_limit`] endpoint was sent.

Rate limits can also be obtained from the response of the [`/table`] endpoint
via `$rate_limit`.
This will display the rate limits in the same format as `sc_rate_limit_table()`
and reflects the rate limit when the table was requested.
No additional API requests are necessary if the rate limit is obtained in this way.

```{r}
table <- sc_table(sc_example("population_timeseries.json"))
table$rate_limit
```

STATcube uses caching for the [`/table`] endpoint by default. If the same
request to `sc_table()` is sent several times, this will not count
towards the rate-limit (100 requests per hour).

[`/info`]: https://docs.wingarc.com.au/superstar/9.12/open-data-api/open-data-api-reference/info-endpoint
[`/rate_limit`]: https://docs.wingarc.com.au/superstar/9.12/open-data-api/open-data-api-reference/rate-limit
[`/schema`]: https://docs.wingarc.com.au/superstar/9.12/open-data-api/open-data-api-reference/schema-endpoint
[`/table`]: https://docs.wingarc.com.au/superstar/9.12/open-data-api/open-data-api-reference/table-endpoint
