---
title: "Other REST API Endpoints"
description: >
  How to use the (rather simple) endpoints `/info`, `/rate_limit_table` and
  `/rate_limit_schema`.
link_text: "other API endpoints article"
---

```{r, echo = FALSE}
source("R/setup.R")$value
```

```{r, include = FALSE}
if (!sc_key_exists())
  knitr::opts_chunk$set(eval = FALSE)
```

Apart form [`/table`] and [`/schema`], there is also support for the simple
endpoints [`/info`] and [`/rate_limit`].

## Server Information

The  [`/info`] endpoint gives and overview about the available languages on the server.

```{r, eval = FALSE}
sc_info()
```

```{r, echo = FALSE}
data.frame(locale = c("de", "en"), displayName = c("Deutsch", "English")) %>% 
  `class<-`(c("tbl", "data.frame"))
```

## Rate Limits (Table)

The [`/rate_limit`] endpoint shows the number of calls to the [`/table`]
endpoint that are remaining. 

```{r, eval = FALSE}
sc_rate_limit_table()
```

```{r}
## remaining: 92/100
## reset:     2022-08-30 13:53:55
```

In this case, we see that 8 out of the 100 requests per hour have been used up
and 92 are still available.
The rate limit will be reset once per hour.
In this case this will be at `2022-08-30 13:53:55`.
The entry under reset should always be less than one
hour after the request to the [`/rate_limit`] endpoint was sent.

## Rate Limits (Schema)

Schema requests are currently limited to 10000 requests per hour.
The number of remaining requests can be obtained via `sc_rate_limit_schema()`.
Rate limits are be returned in the same format as in `sc_rate_limit_table()`.

```{r, eval = FALSE}
sc_rate_limit_schema()
#> remaining: 10000/10000
#> reset:     2022-08-31 17:51:01
```

## Rate Limits from headers

All responses from the STATcube API contain rate limit information (including remaining requests) in the response headers^[Responses for unauthorized requests (response status 401) are an exception].
So instead of using the `/rate_limit*` endpoints shown above, it is also possible to use responses from other endpoints and extract rate limit information from their headers.

The function `sc_rate_limits()` does just that. 
Any return value from `sc_table()`, `sc_table_saved()` and `sc_table_custom()` can be passed to `sc_rate_limits()` and the rate limits will be extracted from the response headers.

```{r}
sc_example("population_timeseries.json") %>% 
  sc_table() %>% 
  sc_rate_limits()
```

Note that the function gives rate limits for `/schama` and `/table` even tough only the `/table` endpoint was used.

The function also works with return values from `sc_schema()` and friends.

```{r}
sc_schema_catalogue() %>% 
  sc_rate_limits()
```

## Server-Side Caching

~~STATcube uses caching for the [`/table`] endpoint by default. If the same
request to `sc_table()` is sent several times, this will not count
towards the rate-limit (100 requests per hour).~~ 

Server-Side caching of [`/table`] responses is currently disabled due to security reasons.
Therefore, all requests against the [`/table`] endpoint count towards the ratelimit.

[`/info`]: https://docs.wingarc.com.au/superstar/9.12/open-data-api/open-data-api-reference/info-endpoint
[`/rate_limit`]: https://docs.wingarc.com.au/superstar/9.12/open-data-api/open-data-api-reference/rate-limit
[`/schema`]: https://docs.wingarc.com.au/superstar/9.12/open-data-api/open-data-api-reference/schema-endpoint
[`/table`]: https://docs.wingarc.com.au/superstar/9.12/open-data-api/open-data-api-reference/table-endpoint
