---
title: "Handling API Errors"
description: >
  STATcubeR converts all http errors into R errors.
  This atricle explains how this conversion happens and showcases some common error messages.
link_text: "error handling article"
---

```{css, echo = FALSE}
pre, pre code {
  white-space: pre;
  padding-right: 1rem;
}
```

```{r, echo=FALSE}
source("R/setup.R")$value
```

This article explains how `r STATcubeR` deals with situations where the communication with the STATcube REST API leads to exceptions such as error codes.

## Throw all the Errors

All http errors codes from the REST API will be turned into R errors.
More precisely, the following conditions are checked to determine wether a request to the STATcube API was successful

* The response returns `FALSE` for `httr::http_error()` which means the response
  status is less than 400. See the [MDN reference] for more information about http status codes.
* The content type of the response is "application/json".

If at least one of those two conditions is not met, an error is thrown.
This is different from the approach taken by other API clients, which will retry requests after certain timeouts or return an "error object".

## Get details about errors

If you encounter an error, you can get more details via `sc_last_error()` or `sc_last_error_parsed()`.
This will return the (parsed) response object that triggered the error.

```{r, eval=FALSE}
sc_info(key = "wrong key")
#> Error: Client error: (401) Unauthorized ...
sc_last_error_parsed() %>% str()
```

```{r, include=FALSE}
try(readRDS("sc_last_error/invalid_key.rds") %>%
  STATcubeR:::sc_check_response())
```

```{r, echo=FALSE}
sc_last_error_parsed() %>% str()
```

`sc_last_error()` returns the same response but in the format returned by `httr::GET()`.
It is more flexible than `sc_last_error_parsed()` but requires you to parse the object yourself.
See `?httr::content` to and `?httr::headers` to get started.

## Common Errors

This section showcases the most common types of errors that you might encounter when interacting with the API.
Please feel free to open a new issue on the [STATcubeR issue tracker] if you get an error which is not listed here.

### Invalid API Key

If an invalid API key is used for a request, a 401 status is returned.

```{r, eval = FALSE}
sc_schema_info(key = "wrong key")
```

```{r, echo = FALSE, error=TRUE}
readRDS("sc_last_error/invalid_key.rds") %>% STATcubeR:::sc_check_response()
```

This example passes the API key as a parameter for simplicity.
In practice, you should set up your key according to the `r ticle('sc_key')`.

### API Not Accessible

This occurs if `r STATcubeR` tries to send requests to a server which is not accessible for the current environment. This will result in a timout error.

```
Error in curl::curl_fetch_memory(url, handle = handle) : 
  Timeout was reached: [${server}] Resolving timed out after 10000 milliseconds
```

Outside of the Statistics Austria firewall, the only working base URL is the following.

```{r}
STATcubeR:::base_url()
```

Reasons this error might occur

1. Your package Version of `r STATcubeR` is outdated (version < 0.4.0)
2. Your company uses a firewall that blocks API requests from leaving.
3. You manually set the `server` parameter in one of the API functions (`sc_table()`, `sc_schema()`, ...)
   to something other than `"ext"`.
4. (Statistics Austria Employees only) You downloaded a json request from one of our internal STATcube
   servers and try to use this request with `sc_table()` from outside.
   
Note to future-self: It might be a good idea to set up some environment variables on Statistic Austrias internal R servers to avoid (3) and (4).

### Rate Limit Exceeded

If the rate limit for the amount of requests against the `/table` endpoint is exceeded, the following error will be shown.

```{r, eval = FALSE}
sc_table_saved("defaulttable_deake005")
```

```{r, echo = FALSE, error=TRUE}
readRDS("sc_last_error/rate_limit.rds") %>% STATcubeR:::sc_check_response()
```

If you encounter this error, please check if the rate limits are in fact a plauible reason by using `sc_rate_limit_table()`.
Unfortunately, the response for exceeded rate limits is very generic and can not be differentiated from the response for invalid json-bodies (see below).
This is why the error message lists two possible reasons.

### Schema

Invalid URIs used with `sc_schema` will be displayed with a special error type `SCHEMA_COMPONENT_NOT_FOUND`.

```{r, eval = FALSE}
sc_schema("invalid_uri")
```

```{r, echo = FALSE, error=TRUE}
readRDS("sc_last_error/schema.rds") %>% STATcubeR:::sc_check_response()
```

### Saved Tables

As mentioned in the `r ticle("sc_table_saved")`, the function `sc_table_saved()`
can only access default tables and tables that are saved under the current user.
If an invalid table URI is passed, the server will respond with a status code of 400.

```{r, eval = FALSE}
sc_table_saved("invalid_uri")
```

```{r, echo = FALSE, error=TRUE}
readRDS("sc_last_error/table_saved.rds") %>% STATcubeR:::sc_check_response()
```

### Invalid JSON

If a request against the `/table` endpoint uses an invalid URI in the json body,
this will trigger a content-type error.
To showcase this, `sc_table()` is used. 
However, invalid URIs that are used with `sc_table_custom()` will throw the same error.

```{r, eval = FALSE}
readLines("request.json") %>% cat(sep = "\n")
```

```json
{
  "database": "str:database:detouextregsai",
  "measures": [ "str:measure:detouextregsai:F-DATA1:INVALID" ],
  "dimensions": [[ "str:field:detouextregsai:F-DATA1:C-SDB_TIT-0" ]]
}
```

```{r, eval = FALSE}
sc_table("request.json")
```

```{r, echo = FALSE, error = TRUE}
readRDS("sc_last_error/invalid_json.rds") %>% STATcubeR:::sc_check_response()
```

Unfortunately, the response for invalid json bodies is very generic and can not be differentiated from the response for exceeded rate limits (see above).
This is why the error message lists two possible reasons.

If you encounter this error during the workflow described in the `r ticle("sc_table")`, it is very likely caused by exceeded rate limits.
This is because json request that are downloaded by the STATcube GUI should always contain valid URIs.
However, if you either modify the downloaded json requests or use `sc_table_custom()`, the reason "invalid json body" is plausible.

## Custom Error Handling

If you want to use your own error-handling instead of the default `r STATcubeR` error handlers, you can get started with the following code sample from one of our `{shiny}` applications.

```{r, eval = FALSE}
shiny::observeEvent(input$button_load_data, {
  table <- try(STATcubeR::sc_table_saved(input$id))
  if (inherits(table, "try-error"))
    STATcubeR::sc_last_error_parsed() %>%
    myApp::show_error_prompt()
  else
    as.data.frame(table) %>%
    myApp::process_data()
})
```

`try()` will turn errors into "error-objects" of class `"try-error"`.
A conditional is then used to perform different actions for successfull and unsccessfull requests.
If an error occurs, the error details are fetched via `sc_last_error_parsed()` and then sent to an error handler.
Otherwise, the return value from `sc_table_saved()` is processed by the success handler.

[MDN reference]: https://developer.mozilla.org/en-US/docs/Web/HTTP/Status?retiredLocale=de
[STATcubeR issue tracker]: https://github.com/statistikat/STATcubeR/issues
