---
title: "Metadata with the Schema Endpoint"
description: >
  The `/schema` endpoint of the REST API provides metadata about databases and
  can also be used to retrieve a catalogue with all available databases
link_text: "schema article"
---

```{r, echo = FALSE}
source("R/setup.R")$value
```

There are currently three functions in `r STATcubeR` that utilize the `/schema`
endpoint.

* `sc_schema_catalogue()` returns an overview of all available databases and tables.
* `sc_schema_db()` can be used to inspect all fields and measures for a database.
* `sc_schema()` returns metadata about any resource.

## Browsing the Catalogue

The first function shows the catalogue, which lists all available
databases in a tree form. The tree structure is determined by the API and
closely resembles the "Katalog" view in the GUI.

```{r}
my_catalogue <- sc_schema_catalogue()
my_catalogue
```

We see that the catalog has 8 child nodes: Four childs of type `FOLDER` and four childs of type `TABLE`.
To get access to the child nodes use `my_catalogue${child_label}`

```{r}
my_catalogue$Statistics
```

The child node `Statistics` is also of class `sc_schema` and shows all entries of the subfolder.
Inside the catalogue, the leafs of the tree are mostly of type `DATABASE` and `TABLE`.
Here is an example for a `TABLE` node.

```{r}
my_catalogue$Statistics$`Labour Market`$`Standardtabelle / Default table (defaulttable_deake005)`
```

As suggested by the output, tables can be used with the `/table` endpoint via `sc_table_saved()`.
See the `r ticle("sc_table_saved")` for more details.

Here is an example for a `DATABASE` node.

```{r}
my_catalogue$Statistics$`Labour Market`$`Working hours (Labour Force Survey)`
```

## Database infos

To get information about a specific database, you can pass the database `id` to `sc_schema_db()`.
Again, the contents do have a tree structure which is similar to the sidebar of the "Tabellenansicht" view.

```{r load_data}
my_db_info <- sc_schema_db("deake005")
my_db_info
```

`my_db_info` can be used in a similar fashion as `my_catalogue`
to obtain details about the resources in the tree. For example, the
`VALUESET` with the label "Gender" can be viewed like this.

```{r}
my_db_info$`Demographic Characteristics`
my_db_info$`Demographic Characteristics`$Gender$Gender
my_db_info$`Demographic Characteristics`$Gender$Gender$male
```

The leafs of database schemas are mostly of type `VALUE` and `MEASURE`.

## Data structure od sc_schema objects

As shown above, `sc_schema` objets have a tree like structure.
Each `sc_schema` object has `id`, `label`, `location` and `type` as the last four entries

```{r}
str(tail(my_db_info$`Demographic Characteristics`, 4))
str(tail(my_catalogue$Statistics, 4))
```

Schema objects can have an arbitrary amount of childs.
Childs are always of type `sc_schema`.
`x$type` determines the type of the schema object.
See the [SuperSTAR API documentation](https://docs.wingarc.com.au/superstar/9.11/open-data-api/open-data-api-reference/schema-endpoint) for a complete list of schema types.

## Other resources

Information about resources other than databases and the catalogue can
be obtained by passing the resource id to `sc_schema()`.

```{r}
my_db_info$Facts$id
group_info <- sc_schema(my_db_info$Facts$id)
group_info
```

Note that the tree returned only has depth 1, i.e. the child nodes of measures are not available in `group_info`. 
However, ids of the child nodes can be obtained with `$id`.
These ids can be used to send another request to the `/schema` endpoint

```{r}
group_info$GEWTATJAHR$id
```

Alternatively, use the `depth` parameter of `sc_schema`.

```r
group_info <- sc_schema(my_db_info$Facts$id, depth = "valueset")
```

## Printing with data.tree

If the `{data.tree}` package is installed, it can be used for an alternative
print mehtod.

```{r}
print(my_catalogue, tree = TRUE)
```

The data.tree implementation can be set as a default with `options()`

```{r}
options(STATcubeR.print_tree = TRUE)
my_catalogue$Statistics
```



