---
title: "Schema"
description: >
  The /schema endpoint of the REST API provide metadata about databases and
  can also be used to retrieve a catalogue with all available databases
link_text: "schema article"
---

```{r, echo = FALSE}
source("R/setup.R")$value
```

There are currently three functions in `{STATcubeR}` that utilize the `/schema`
endpoint.

* `sc_schema_catalogue()` returns an overview of all available databases and
  tables.
* `sc_schema_db()` can be used to inspect all fields and measures for a
  database.
* `sc_schema()` returns metadata about any resource.

All functions return tree-like objects that are printed with the `{data.tree}`
package.

## Browsing the Catalogue

The first function shows the catalogue, which lists all available
databases in a tree form. The tree structure is determined by the API and
closely resembles the "Katalog" view in the GUI.

```{r}
my_catalogue <- sc_schema_catalogue()
my_catalogue
```

Now `my_catalogue` can be used to obtain database ids.

```{r}
my_catalogue$Statistics$`Labour Market`
my_catalogue$Statistics$`Labour Market`$`Working hours (Labour Force Survey)`
```

## Database infos

To get more information about this database, you can pass the `id` to
`sc_schema_db()`. Again, the contents do have a tree structure which is
similar to the sidebar of the "Tabellenansicht" view.

```{r load_data}
my_db_info <- sc_schema_db("deake005")
my_db_info
```

`my_db_info` can be used in a similar fashion as `my_catalogue`
to obtain details about the resources in the tree. For example, the
`VALUESET` with the label "Gender" can be viewed like this.

```{r}
my_db_info$`Demographic Characteristics`
my_db_info$`Demographic Characteristics`$Gender$Gender
my_db_info$`Demographic Characteristics`$Gender$Gender$male
```

## Other resources

Information about resources other than databases and the catalogue can
be obtained by passing the resource id to `sc_schema()`.

```{r}
my_db_info$Facts$id
group_info <- sc_schema(my_db_info$Facts$id)
group_info
```

Note that the tree returned only has depth 1, i.e. the child nodes of measures
are not returned. However, ids of the child nodes can be obtained with `$id`.

```{r}
group_info$GEWTATJAHR$id
```

