---
title: "Custom Tables"
description: >
  Define custom requests against the `/table` endpoint by defining ids of
  requested resources as character vectors.
---

```{r, include = FALSE}
pkgload::load_all(export_all = FALSE, reset = FALSE, helpers = FALSE) 
```

```{r}
source("R/add_tooltip.R")$value
```

Another way to import STATcube Data into R is the use of a custom table. This
function requires the three arguments.

* A database id
* ids of measures to be imported (type `MEASURE` or `STAT_FUNCTION`)
* ids of fields to be imported (type `FIELD` or `VALUESET`)

Based on the database id, the remaining ids can be obtained with `sc_schema()`.
See the `r ticle('sc_schema')` for more details.

```{r, cache = TRUE}
id_db <- "str:database:detouextregsai"
db_schema <- sc_schema_db(id_db)
db_schema
```

Browse the schema to extract the desired ids. The basic idea is to extract the
id components of desired measures and fields. If a measure has more than one
entry of type `STAT_FUNCTION` either use the id of the measure to utilize
the default function or provide the id of the function. The same is true if
a field has several `VALUESET`s

```{r}
get_id <- function(x) {print(c(x$type, x$id)); x$id}
id_arrivals <- get_id(db_schema$Facts$Arrivals$Arrivals)

id_nights_spent <- get_id(db_schema$Facts$`Nights spent`)

id_time <- get_id(db_schema$`Mandatory fields`$`Season/Tourism Month`)

id_region <- get_id(db_schema$`Other Classifications`$`Country of origin`$`Herkunftsland (Ebene +1)`)
```
Now the ids can be used in `sc_table_custom()`. If several ids are used for the
argument `dimensions` or `fields`, combine them with `c()` to pass a character
vector of ids.

```{r}
my_response <- sc_table_custom(
  db = id_db,
  measures = c(id_arrivals, id_nights_spent),
  dimensions = c(id_time, id_region)
)
my_response
```


