---
title: "Tabulating STATcubeR Datasets"
description: >
  Learn how to turn sc_table objects into tidy data frames using the
  tabulate() method.
link_text: "tabulation article"
---

```{r, echo = FALSE}
source("R/setup.R")$value
```

```{r, include = FALSE}
options(tibble.print_min = 5)
cancer   <- od_table("OGD_krebs_ext_KREBS_1")
earnings <- od_table("OGD_veste309_Veste309_1")
```

This article contains the most important aspects of the method `$tabulate()`.
This method aggregate s`sc_data` objects.
The first part will use the `r tippy_dataset(cancer, "cancer dataset")` from the `r ticle("od_table")`.
After that, other features of `$tabulate()` will be demonstrated with the data from the `r tippy_dataset(earnings, "structure of earnings survey (SES)")`.

```{r, eval = FALSE}
cancer   <- od_table("OGD_krebs_ext_KREBS_1")
earnings <- od_table("OGD_veste309_Veste309_1")
```

Notice that these tabulation methods can also be used with the STATcube REST API.
This means that objects created by `sc_table()` also have a `$tabulate()` method.

## Tabulating Data {#tabulate}

Calling the `$tabulate()` method with no arguments produces a table with the same dimensions as `$data`.

```{r}
cancer$tabulate()
```

```{r}
identical(dim(cancer$tabulate()), dim(cancer$data))
```

Instead of `cancer$tabulate(...)` it is also possible to use `sc_tabulate(cancer, ...)`.
All available parameters for the `$tabulate()` method are documented in `?sc_tabulate`.

## Aggregation

### Aggregating with sums

To get the number of cases by reporting year and sex, use the labels of those variables as arguments.

```{r}
cancer$tabulate("Reporting year", "Sex")
```

If more than one measure is included in the dataset, all measures will be aggregated.
`r STATcubeR` uses `rowsum()` to ensure a good performance with big datasets.
It is also possible to use partial matching or use codes.

```{r}
cancer$tabulate("Reporting", "C-KRE")
```

`r STATcubeR` will use `pmatch()` to match the supplied strings with the metadata
to identify the variables that should be used for aggregation.

### Limitations of sums {#totals}

In some cases, datasets cannot be aggregated using the `rowsum()` approach.
As an example, take the structure of earnings survey.

```{r}
earnings <- od_table("OGD_veste309_Veste309_1")
earnings
```

As we can see from the `print()` output, the measures contain means and quartiles.
Therefore, aggregating the data via `rowsum()` is not meaningful.
However, this dataset contains a "total code" for every field.

```{r, echo = FALSE}
options(tibble.print_min = 10)
```

```{r}
earnings$tabulate()
```

### Aggregating via total codes

These total codes can be used to aggregate the data with `$tabulate()`.
In order to do that, the total codes need to be specified using `$total_codes()`. 

```{r}
earnings$total_codes(Sex = "Sum total", Citizenship = "Total", 
                     Region = "Total", `Form of employment` = "Total")
```

Now `$tabulate()` will use these total codes to form aggregates of the data.

```{r}
earnings$tabulate("Form of employment")
```

As we can see, the method extracted rows 2 to 7 from the data. The logic for
selecting those rows is equivalent to the following `{dplyr}` expression.

```{r, eval = FALSE}
earnings$data %>% dplyr::filter(Sex == "Sum total" & Citizenship == "Total" & 
  `Region (NUTS2)` == "Total" & `Form of employment` != "Total") %>% 
  dplyr::select(-Sex, -Citizenship, -`Region (NUTS2)`)
```

The `$tabulate()` method also works with more than one variable.

```{r, echo = FALSE}
options(tibble.print_min = 12)
```

```{r}
earnings$tabulate("Sex", "Form of employment")
```

### Including totals in the oputput

It is not necessary that all fields have totals.
For example, suppose we want to include the totals for `Sex` in the output table.
We can just remove the toal code before running `sc_tabulate()`.
The special symbol `NA` can be used to unset a total code.

```{r}
earnings$total_codes(Sex = NA)
earnings$tabulate("Sex")
```

## German Labels and Codes

For OGD datasets, it is possible to switch the language used for labeling the data.
This can be done by setting `$language` to `"de"` or `"en"`.

```{r}
earnings$language <- "de"
earnings$tabulate("Geschlecht")
```

To skip labelling altogether and use variable codes in the output, use `raw=TRUE`.

```{r}
earnings$tabulate("Geschlecht", raw = TRUE)
```

Switching languages is currently only available for `od_table()` objects.
For `sc_table()` objects this would require more support for the `sc_schema()` endpoint.
See the [github issues] for some development goals regarding labeling.

## Subsetting columns

In the previous examples, we only supplied names ando/or codes of fields to `sc_tabulate()`.
It is also possible to include measures in which case the unlisted measures will be omitted.

```{r}
earnings$tabulate("Geschlecht", "Arithmetisches Mittel", "2. Quartil")
```

Just like for fields, measures also support partial matching and codes.
In the above example, `"2. Quartil"` was matched to `"2. Quartil (Median)"`.

## Programmatic usage

Notice that we used the german label for the column `"Sex"` in the last calls
to `tabulate()`. This is necessary because only the "active" labels are
available to define the tabulation. If you want to use `r STATcubeR`
programatically, always use codes to define the tabulation and also use the
`.list` parameter if you want to pass several codes.

```{r, echo = FALSE}
options(tibble.print_min = 7, tibble.print_max = 7)
```

```{r}
earnings$field("C-A11-0")
earnings$total_codes(`C-A11-0` = "A11-1")
vars_to_tabulate <- c("C-A11-0", "C-BESCHV-0")
earnings$tabulate(.list = vars_to_tabulate)
```

`$total_codes()` currently uses an ellipsis (`...`) parameter to define total codes.
In the future, programmatic updates of `sc_data` objects should be defined in `$recodes`.
See [#17](https://github.com/statistikat/STATcubeR/issues/17).

[github issues]: https://github.com/statistikat/STATcubeR/labels/label
