---
title: "Schema"
---

```{r, include = FALSE}
pkgload::load_all(export_all = FALSE, reset = FALSE, helpers = FALSE) 
knitr::opts_chunk$set(cache = TRUE)
```

There are currently two functions in `STATcubeR` that utilize the `/schema`
endpoint. The first function shows the catalogue, which lists all available
databases in a tree form. The tree structure is determined by the API and
closely resembles the "Katalog" view in the GUI.

```{r}
my_catalogue <- sc_catalogue()
print(my_catalogue, limit = 20)
```

Now `my_catalogue$parsed` can be used to obtain database ids.

```{r}
my_catalogue$parsed$Statistiken$Tourismus$`Nächtigungsstatistik ab 1974 nach Kalenderjahr`
```

To get more information about this database, you can pass the `id` to
`sc_db_info()`. Again, the contents do have a tree structure which is
similar to the sidebar of the "Tabellenansicht" view.

```{r load_data, chache = TRUE}
my_db_info <- sc_db_info("detouextkal")
my_db_info
```

`my_db_info$parsed` can be used in a similar fashion as `my_catalogue$parsed`
to obtain details about the resources in the tree.

```{r}
my_db_info$parsed$`Weitere Klassifikationen`$Herkunftsland[1:4]
```

